Formal Verification of Real Models from Platforms Using The B-method

### 2009-04-25 trunk/papers/FM2009/source/paper.tex
Proofs finished

[Conclusao] Este projeto tem um grande número provas e o processo de prova eh uma das etapas que consomem
maior tempo. Para concluir o processo de prova de todo o microcontrolador foi demando um grande tempo,
aproximadamente um mês. Isto foi custoso, porque foi necessário elaborar, retificar e provar várias lemmas
dos projetos de base, Hardware and Types Library. Entretanto, com os projetos básicos mais maduros,
torna-se bem mais rápida a modelagem e verificação de um novo microprocessador\footnote{Actualy, the
microprocessors M8051 and PIC16F432 are under construction}.

Com os projetos de base completamente provados, então aproximadamente 89\% das provas não obvias e 55\% da
Proofs WD foram realizadas automaticamente. As demais provas foram realizadas após o uso de alguns passos
de prova\footnote{Passos de prova são comandos que indicam um caminho para o provador concluir a prova,
esses comandos apenas indicam um caminho, ou seja, ele não introduzem hipósteses falsas} associados a
pattern matching of proof obligations. The user pass associeted to match pattern  aceleraram bastante o
processo de prova, pois existem muitas instruções do microcontrolador com caractéristicas semelhantes e o
atelierb é capaz de re-usar os passos de prova. Então, poucos passos de prova podem ser úteis para uma
grande variedade de provas. Um exemplo é o conjunto de 17 passos de prova que rapidamente ajudou a
verificar 99\% (2295) das provas WD. A experiência em adicionar passos de prova também ajudou a reduzir o
tempo do processo de prova em mais de 90\%. Isso aconteceu, porque o uso de passos de prova direciona melhor o
provador ao fim da prova.

To further reduce cost of proof process, a new feature supported by AtelierB was used, the
parallelization. To do this were used three computers each one with two cores, the that theoretically
increased by six times the capacity of processing.

A special care was taken to represent the model in way simple and accurate. This care also reduced the number of
proofs. Because, the simple act of optimizing the use the simple act of optimizing the use of
override operator ($\lover$) fell too the number of proof obligations.

>>>>

% [Conclusao]
This project has many proof obligations and its process of verification is the step of the most time consumed. The
verification step of all the model spent about a month. This was hard, because was necessary to build, correct and
prove several expressions from basic projects, Hardware and Types Library. However, when the basic projects are
ready, the modelling and verification of new plataform \footnote{Actualy, the microprocessors M8051 and PIC16F432
are under construction} become more fast and easy. Thus, these basic projects were also built to re-use to other
platforms. When the basic projects are ready, then about 89\% proof non obvious and 55\% of Proofs WD was conclused
automaticly.

The others were concluded through the use of proof commands\footnote{The proof commands are step that just indicate
a walk to prover make the proof, thus, theses commands cannot introduce false hypotheses.} associated to match
pattern from proof obligations. The match pattern accelerates too much the prove process, because there are many
similar assembler instructions and the AtelierB can re-use the match pattern and its proof commands associated.
Therefore, few proof commands can be useful to many obrigações de prova. A good example is a set of 17 proof
commands that fastly helps to verify 99\% (2295) of proofs WD. To further reduce cost of proof process, a new feature
supported by AtelierB was used, the parallelization. To do this were used three computers each one with two cores,
the that theoretically increased by six times the capacity of processing.

A special care was taken to represent the model in way simple and accurate. This care also reduced the number of
proofs. Because, the simple act of optimizing the use of override operator ($\lover$) fell too the number of proof
obligations.
